Types for R, Empirically Designed and Evaluated

### 2020-05-08 paper/main.tex
initial class discussion

@@

%
%
%
%
%
%
\section{Evaluation Results}

@@

\section{Related Work}

@@

\section{Conclusion}

@@

\subsection{Threats to Validity}

@@

\subsection{Future Work}

>>>>

Another pattern that we observed was the use of consistently-named lists.
In R, ``fields'' of named lists can be accessed using the \code{$} operator, such as:
\begin{lstlisting}
p <- list(x=1, y=2)
p$x + p$y
\end{lstlisting}
We thought to capture this type of behaviour with a {\it struct} type, such as \code{struct<x: integer, y: integer>}.
Initial analyses suggested that structs were very common, but further inspection revealed that they failed to tell the full story.
For instance, \AT{many} structs were merely representing list-typed values with a {\it class}, and we could capture these types more succinctly with a class-based type.
Further, it is common in R example code to use some built-in data sets, such as \AT{mention some}.
These caused undue noise, as even with our struct name unification strategy, poorly tested functions appeared to operate on e.g. \AT{funny struct type from the previous data set}.
Ultimately, we found that sticking to list types and adding a class-based was the wisest course of action.
We will discuss class types shortly.

@@

Speaking of classes, an important classful value in R is the data frame.
Data frames underpin nearly all idiomatic use of the language, and even popular \code{tibble} (from the \code{tidyverse} ecosystem) and \code{data.table} (from the \code{data.table} package) build on the essential type.
We entertained the possibility of including data frame types, but \AT{found them to be clunky? Question mark?}
Consider: \AT{example of why data.frame types would be bad atm.}

Data frames do have a type, through the \code{class<data.frame>} type, and future work will expand on this type, discussed further in Section~\ref{sec:futurework}.

%
%
%
%
\subsection{Classes in R}

\AT{Fill in.}

%
%
\subsubsection{Class Types}

\AT{We have classes.}

%
%
\subsubsection{Multi-Classes}

\AT{We support multiple classes on values.}

%
%
\subsubsection{Forgoing R's Object Systems}

\AT{Roughly: too complicated. We have rudimentary class types for S3, and an S4 type for S4.
Future work will explore further.}

%
%
%
%
%
%
\section{Evaluation Results}
\label{sec:evaluation}

@@

%
%
%
%
%
%
\section{Related Work}
\label{sec:relatedwork}

@@

%
%
%
%
%
%
\section{Conclusion}

@@

%
%
%
%
\subsection{Threats to Validity}
\label{sec:threatstovalidity}

@@

%
%
%
%
\subsection{Future Work}
\label{sec:futurework}
